\subsection{Controller}

The controller is a Python script that takes as input the car's current
lane, intended lane, velocity, and booking status, and outputs an
instruction in the form of a new velocity and delay. This instruction
implies that the car will stop at the intersection for $delay$ seconds, and
then proceed to continue along its intended path at a constant speed given
by new velocity. The controller guarantees that the car's trajectory,
assuming the instruction is properly followed, will be collision-free. The
controller receives requests and sends commands almost instantaneously to
system vehicles. For convenience in calculations, the controller also takes
as input the current time.

For a somewhat more realistic simulation, we decided to add a delayed
feedback to the controller output. Not only does this prevent a causality
loop and Zeno system, but it also models a real-life communication delay
between the controller and the vehicles. The controller also has a $id$
output, which enables multiplexer-like functionality such that the
controller is able to communicate with a particular vehicle in the
MultiInstanceCompositeActor.

The scheduling algorithm employed by the controller is as follows:

\begin{framed}
\centering\small
\begin{algorithmic}
\State {Initialize list of conflict zones and displacements along paths}
\For{each timestep $t$}
	\State $current \gets \text{all tokens received from Vehicle modal model}$
	\For{each $car$ in $current$}
		\If{$car$ needs reservation}
			\State {$v_\text{max} \gets$ maximum velocity
				$\in [ v_\text{current} \pm 10 ]$ that ensures safety}
			\If{$v_\text{max}$ exists}
				\State $v_\text{new} \gets v_\text{max}$
				\State $t_\text{delay} \gets 0$
			\Else
				\State $v_\text{new} \gets v_\text{current} + 10$
				\State $t_\text{delay} \gets$ end of latest reservation for all conflict zones
			\EndIf
			\State broadcast($v_\text{new}$, $t_\text{delay}$,
					$\text{id} \gets car\text{.id}$)
		\EndIf
	\EndFor
\EndFor
\end{algorithmic}
\end{framed}
